### 2022-10-14 manuscript.Rmd
Fix TFR units

  # Fit an additional model for event-related power, controlling for RTs
  form_rt <- ~ phase * condition + log(rt) +
    (phase * condition | participant_id) +
    (phase * condition | item_id)
  models_control$alpha_beta <-
    fit_mixed_models(form = form_rt, data = trials_main, dep = "alpha_beta")

>>>>

  # Fit an additional model for event-related power, controlling for RTs
  trials_main$alpha_beta <- trials_main$alpha_beta * 100 # Convert to percent
  form_rt <- ~ phase * condition + log(rt) +
    (phase * condition | participant_id) +
    (phase * condition | item_id)
  models_control$alpha_beta <-
    fit_mixed_models(form = form_rt, data = trials_main, dep = "alpha_beta")
